---
title: "Now it goes"
author: "Fabio L. C. Barbosa"
date: "8/6/2020"
output: ioslides_presentation
---

## Preparing the grounds - sexy title

```{r}
library(tidyverse)
library(readr)
library(lubridate)
library(ggplot2)
library(plotly)

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r}

fixed.ds <- read_csv("fixedds.csv")
```


## Slide with Plot2
```{r, echo=FALSE, message=FALSE}

COVID_TABLE <- fixed.ds %>% group_by(DATE = date(ATOT), CLASS) %>% summarise(N_FLT =  n(),.groups="drop") %>% filter(!is.na(CLASS))

COVID_CURVE <- COVID_TABLE %>% ggplot() +
  geom_line(aes(x = DATE, y = N_FLT , color = CLASS)) +
  labs(title = "Brazil Air Traffic", subtitle = "COVID effect (per day)", x = "Date", y = "Flights", caption = "Developed by Fábio Barbosa") +
  #facet_wrap(.~CLASS) +
  theme_minimal ()
ggplotly(COVID_CURVE)
```

